Unknown

### 2025-06-25 ms/ms.qmd
lma-aa figure

<!-- Paragraph 7 (summarize secondary results) -->
The pattern of AA across wild tomatoes strongly supports the plasticity hypothesis, argues against the acclimatory hypothesis, and provides only weak support for the constitutive hypothesis. Plastic changes in leaf thickness and/or packing density, summarized by the bulk leaf mass per area (LMA), likely mediate the effect of growth light intensity on AA. When LMA is included in the model, the effect of growth light intensity on AA is no longer significant based on model comparison (Table ? - need to check out what the interaction with measurement light intensity means). In contrast, LMA did not mediate indirect effects of native PAI on AA (Table ?). Many anatomical traits underlie LMA [@john_anatomical_2017] and future research will be needed identify which particular traits, such as leaf thickness or mesophyll porosity, are responsible for mediating AA.

>>>>

<!-- Paragraph 7 (summarize secondary results) -->
The pattern of AA across wild tomatoes strongly supports the plasticity hypothesis, argues against the acclimatory hypothesis, and provides only weak support for the constitutive hypothesis. Plastic changes in leaf thickness and/or packing density, summarized by the bulk leaf mass per area (LMA), likely mediate the effect of growth light intensity on AA. LMA increased in sun grown plants in all accessions by an average of X% [CI], similar to plastic responses in many species [@poorter_metaanalysis_2019]. When LMA is included in the model, the effect of growth light intensity on AA is no longer significant based on model comparison (Table ? - need to check out what the interaction with measurement light intensity means) and LMA is weakly positively correlated with AA (Figure X). In contrast, LMA did not mediate indirect effects of native PAI on AA (Table ?). Many anatomical traits underlie LMA [@john_anatomical_2017] and future research will be needed identify which particular traits, such as leaf thickness or mesophyll porosity, are responsible for mediating AA.
